Equivalence Testing and the Second Generation \emph{P}-Value

### 2019-03-10 manuscript.R1.Rmd
R1 final resubmission

author_note: |
  All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV. This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.

>>>>

author_note: |
  All code associated with this article, including the reproducible manuscript, is available from https://github.com/Lakens/TOST_vs_SGPV and https://osf.io/8crkg/. The preprint can be found at https://psyarxiv.com/7k6ay/. This work was supported by the Netherlands Organization for Scientific Research (NWO) VIDI grant 452-17-013.
